### 2016-06-23 Appendix.tex
NLO chapter

\subsection{Constants of the Colour Algebra $SU(N)$}
[Marina von Steinkirch]\\
Tha Casimir operator $C(R)\mathbbm{1}$ of a semi-simple Lie algebra in the irreducible representation $R$ is given by
\begin{align}
g^{ab} T^a(R)T^b(R) = C(R)\mathbbm{1} \label{eq:Casimir}
\end{align}
where $T^a(R)$ is the $a$-th generator of the matrix valued representation $R$, $g^{ab}$ is the metric of group, $C(R)$ is the Quadratic Casimir invariant of the representation $R$ and $\mathbbm{1}$ is the identity in the representation space.\\
Apart from $C(R)$ it is common to define the Dynkin-Index $T(R)$:
\begin{align}
\mathrm{Tr}\left[T^a(R)T^b(R)\right] = T(R)\delta^{ab}.
\end{align}
The two constants are connected by
\begin{align}
C(R) \cdot \mathrm{dim}(R) = T(R) \cdot \mathrm{dim}(G)
\end{align}
where $\mathrm{dim}(G)$ is the dimension of the group and $\mathrm{dim}(R)$ is the dimension of the irreducible representation $R$.\\
In the case of $SU(N)$ one has a diagonal metric $g^{ab} = \delta^{ab}$ and therefore \ref{eq:Casimir} turns to
\begin{align}
\sum_a (T^a(R))^2 = C(R)\mathbbm{1}_{\mathrm{dim}(R) \times \mathrm{dim}(R)}
\end{align}
and one can write down the following useful formulae for the fundamental representation $R=F$: $T^a_{ij} = \frac{\lambda^a_{ij}}{2}$ and the adjoint representation $R=A$: $(T^a_{ij})^{adj} = -if_{aij}$
\begin{align}
T^a_{ik} T^a_{kj} &= C(F)\mathbbm{1}_{ij} && \mbox{with}\ C(F) = \frac{N^2-1}{2N} = \frac{4}{3}\nonumber\\
f^{abc} f^{dbc} &= C(A)\delta^{ad} && \mbox{with}\ C(A) = N = 3\nonumber\\
\mathrm{Tr}\left[T^aT^b\right] &= T(F)\delta^{ab} && \mbox{with}\ T(F) = \frac{1}{2}\label{eq:DynkinIndex}
\end{align}
where $\lambda^a_{ij}$ are for $N_c = 3$ the Gell-Mann matrices and $f_{abc}$ are the structure constants of $SU(N_c)$.
%\begin{tabular}{c|c|c}
%Quadratic Casimir Invariant and $T(R)$ & $SU(N)_c$ & $SU(3)_c$\\
%\hline
%$C_2(3)$ & $\frac{N^2-1}{2N}$ & $\frac{4}{3}$\\
%$C_2(8)$ & $N$ & $3$\\
%$T(3)$ & $\frac{1}{2}$ & $\frac{1}{2}$ \\
%$T(8)$ & $N$ & $3$ 
%\end{tabular}

@@

The definition of the Passarino-Veltman integrals in this thesis agrees with the one from \texttt{Looptools} \cite{Hahn:1998} convention. The original paper \cite{Passarino:1978jh} uses slightly different conventions. A pedagogical introduction to the evaluation of one-loop integrals can be found in \cite{Ellis:2011cr}

@@

\frac{i}{16\pi^2} C_{0,\mu,\mu\nu}(p_1^2,p_2^2,(p_1+p_2)^2,m_1^2,m_2^2,m_3^2) &= \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p_1)^2-m_2^2][(l+p_1+p_2)^2-m_3^2]}\nonumber

@@

and Passarino-Veltman decomposition \cite{Passarino:1978jh} one can determine the UV-divergent part of all $B$ and $C$ integrals. In chapter \ref{sec:MSRen} this was necessary in order to obtain the renormalization constants in the $\overline{\mathrm{MS}}$-scheme. Infrared and collinear singularities arise from the special case where one or multiple masses tend to zero. These poles are either regularized in terms of a small mass cutoff $\Lambda$ or also dimensionally as $\epsilon$-poles. In the later case the integral first needs to undergo the limit to zero masses and than being evaluated.\\

>>>>

\subsection{Constants of the Color Algebra $SU(N)$}\label{sec:coloralgebra}
[Marina von Steinkirch]\\
Tha Casimir operator $C(R)\mathbbm{1}$ of a semi-simple Lie algebra in the irreducible representation $R$ is given by
\begin{align}
g^{ab} T^a(R)T^b(R) = C(R)\mathbbm{1} \label{eq:Casimir}
\end{align}
where $T^a(R)$ is the $a$-th generator of the matrix valued representation $R$, $g^{ab}$ is the metric of group, $C(R)$ is the Quadratic Casimir invariant of the representation $R$ and $\mathbbm{1}$ is the identity in the representation space.\\
Apart from $C(R)$ it is common to define the Dynkin-Index $T(R)$:
\begin{align}
\mathrm{Tr}\left[T^a(R)T^b(R)\right] = T(R)\delta^{ab}.
\end{align}
The two constants are connected by
\begin{align}
C(R) \cdot \mathrm{dim}(R) = T(R) \cdot \mathrm{dim}(G)
\end{align}
where $\mathrm{dim}(G)$ is the dimension of the group and $\mathrm{dim}(R)$ is the dimension of the irreducible representation $R$.\\
In the case of $SU(N)$ one has a diagonal metric $g^{ab} = \delta^{ab}$ and therefore \ref{eq:Casimir} turns to
\begin{align}
\sum_a (T^a(R))^2 = C(R)\mathbbm{1}_{\mathrm{dim}(R) \times \mathrm{dim}(R)}
\end{align}
and one can write down the following useful formulae for the fundamental representation $R=F$: $T^a_{ij} = \frac{\lambda^a_{ij}}{2}$ and the adjoint representation $R=A$: $(T^a_{ij})^{adj} = -if_{aij}$
\begin{align}
T^a_{ik} T^a_{kj} &= C(F)\mathbbm{1}_{ij} && \mbox{with}\ C(F) = \frac{N^2-1}{2N} = \frac{4}{3}\nonumber\\
f^{abc} f^{dbc} &= C(A)\delta^{ad} && \mbox{with}\ C(A) = N = 3\nonumber\\
\mathrm{Tr}\left[T^aT^b\right] &= T(F)\delta^{ab} && \mbox{with}\ T(F) = \frac{1}{2}\label{eq:DynkinIndex}
\end{align}
where $\lambda^a_{ij}$ are for $N_c = 3$ the Gell-Mann matrices and $f_{abc}$ are the structure constants of $SU(N_c)$.
%\begin{tabular}{c|c|c}
%Quadratic Casimir Invariant and $T(R)$ & $SU(N)_c$ & $SU(3)_c$\\
%\hline
%$C_2(3)$ & $\frac{N^2-1}{2N}$ & $\frac{4}{3}$\\
%$C_2(8)$ & $N$ & $3$\\
%$T(3)$ & $\frac{1}{2}$ & $\frac{1}{2}$ \\
%$T(8)$ & $N$ & $3$ 
%\end{tabular}

@@

The definition of the momenta within the Passarino-Veltman integrals in this thesis agrees with the one from \texttt{Looptools} \cite{Hahn:1998} convention. The original paper \cite{Passarino:1978jh} uses slightly different conventions. A pedagogical introduction to the evaluation of one-loop integrals can be found in \cite{Ellis:2011cr}.  $A$, $B$ and $C$ integrals are defined by:

@@

\frac{i}{16\pi^2} C_{0,\mu,\mu\nu}(p_1^2,p_2^2,(p_1+p_2)^2,m_1^2,m_2^2,m_3^2) &= \int_l \frac{\left\{1,l_\mu,l_\mu l_\nu \right\}}{[l^2-m_1^2][(l+p_1)^2-m_2^2][(l+p_1+p_2)^2-m_3^2]}.\nonumber\label{eq:LoopInt}

@@

and Passarino-Veltman decomposition \cite{Passarino:1978jh} one can determine the UV-divergent part of all $B$ and $C$ integrals. In chapter \ref{sec:MSRen} this was necessary in order to obtain the renormalization constants in the $\overline{\mathrm{MS}}$-scheme. Infrared and collinear singularities arise from the special case where one or multiple masses tend to zero. These poles can be regularized with a small mass cutoff $\Lambda$ leading singularities of the form $\ln \Lambda$ or dimensionally which leads to $\epsilon$-poles as in the treatment of UV-divergences. In the latter case the integral first needs to undergo the limit to zero masses and than being evaluated.\\
